Project Protocol

### 2019-10-18 protocol.Rmd
outcomes

When participants see the same data set displayed a line up as a hexagon tile map and geographic map, participants will pick the map that displays a pattern influenced by population density more often when the information is presented in a hexagon tile map.

@@

1.	Measure the accuracy in spotting a real population density related spatial distribution from a line-up of null maps
2.	Contrast the accuracy and efficiency when participants pick from geographic or hexagon maps

@@

Experiment information collected:

- Choice of plot in each line up
- Reason for choice of plot
- Time taken to answer
- Perceived difficulty of question

Factors:

- Plot type ( Hexagon / Geographic )
- Spatial dependence structure ( Difference in a single city / Related to population density / North to South )

We will record demographic information to consider the impacts of:

- gender (female / male / other),
- degree education level achieved (high school / bachelors / masters / doctorate / other),
- age range (18-25 / 25-35 / 35-45 / 45-55 / 55+ / other)
- lived in Australia (Yes / No / Other)

@@

The possible levels of the factors are:

@@

##	Data collection
As the survey is conducted through the Figure-Eight platform, the human data will also be collected in the form of an IP address, Contributor ID, Trust Score and Channel. Some sources believe an IP address is identifiable information, as such it will not be held publicly online when the data is held on github. We will also ask for information regarding gender, education level achieved, and age range to understand perception of different groups.

@@

An expansion of the various observations, data and measures that will be made during the study and which will contribute to establishing success or otherwise in addressing the research question.

The collection of multiple responses from each person as they complete several different lineup tasks, allows estimates of their perceptual ability and allows them to correct power differences between competing designs: by modeling power using a subject-specific random intercept in a generalized linear model.

>>>>

A hexagon tile map display allows people to detect the impact of a disease in highly populated small areas with higher accuracy and efficiency, in comparison to the accuracy and efficiency of detections made when viewing a choropleth map.

@@

1. Show that spatial disease trends, that impact highly populated small areas, are detected with higher accuracy when viewed in a hexagon tile map display.

@@

For each plot evaluation the subject will provide these responses:

- Their choice of plot from a lineup
- Reason for choice of plot
- Time taken to respond
- Perceived difficulty in making a choice

@@

The levels of the factors are:

@@

##	Data collection

As the survey is conducted through the Figure-Eight platform, IP Address Contributor ID, Trust Score and Channel(add link to Figure 8 details page ) will be provided. In addition to the experimental design and response variables:

- Plot type ( Hexagon / Geographic )
- Trend model ( Two hotspots / Multiple hotspots / spatial trend )
- Choice of plot in each line up
- Reason for choice of plot
- Time taken to answer
- Perceived difficulty of question

the survey of participants will provide this demographic information:

- Gender (female / male / other),
- Degree education level achieved (high school / bachelors / masters / doctorate / other),
- Age range (18-24 / 25-34 / 35-44 / 45-54 / 55+ / other)
- Lived in Australia (Yes / No / other)

@@

## Response variables

### Accuracy

To measure the accuracy of the detections, the plot chosen for each lineup evaluated will be compared to the position of the real spatial trend plot in the lineup.

A correct result occurs when the chosen plot matches the position of the real plot, this will be recorded in an additional binary variable called $collect$.

The accuracy of the choices for each display will be calculated as a proportion: 
$accuracy = number correct/number shown$.

### Efficiency

High efficiency occurs when a small amount of time is taken to evaluate each lineup.
This will be measured as the inverse of the numeric variable measuring the length of time taken to submit the answers to the evaluation of each line up.

The efficiency of the choices for each display will be calculated by the time taken as a fraction of the maximum time taken by all respondents to respond:
$efficiency = time taken/maximumtime taken$.

## Model

Response Variables:
Accuracy and Efficiency

Design:
We will model the difference between the accuracy and efficiency when evaluating hexagon tile maps and geographic maps.

Random Effects:
The collection of multiple responses from each person as they complete several different lineup tasks, allows estimates of their perceptual ability using a subject-specific random intercept in a generalized linear model.

Cofactors:
responses to the questions regarding the difficulty of making a choice and the reason for the choice of plot in the line up.

Interactions:
